Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-07-21 Paper/Poster/poster.tex
getting close to be ready

\myfig[0]{code_axis.ps}{.4}

@@

\textbf{Beat-Chroma Patches.}
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item We use Echo Nest analysis to break a song into a collection of 
beat-chroma ``patches'', typically one or two bars in length.
\item $82\%$ of the bars in our data were 4 beats long.
\item Other cases: we resample patches to a fixed length of 4 beats.
\item We rotate patches so that the first row contains the most energy.
Each patch is normalized independently.
\end{list}

@@

\myfig[0]{song_encoded.ps}{.9}

\myfig[0]{codes_8bars.ps}{.8}

@@

% figure caption
\begin{center}
\begin{minipage}[c]{.5\columnwidth}
\begin{small}
Possible visualization of the codebook using locally linear
embedding (LLE).
\end{small}
\end{minipage}
\end{center}

>>>>

\vspace{-.3cm}
\makebox[\columnwidth]{ % replace framebox by makebox
\hspace{-4cm}
\begin{minipage}[l]{.78\columnwidth}
\myfig[0]{code_axis.ps}{.45}
\end{minipage}
\hspace{-3cm}
\begin{minipage}[l]{.4\columnwidth}
Typical learned codeword spanning $2$ bars, each bar
considered to be $4$ beats. Codebook size was $200$.
\end{minipage}
} % end framebox / makebox
\vspace{.5cm}

@@

\vspace{.5cm}
\textbf{Beat-Chroma Patches.}
\begin{list}{\labelitemi}{\leftmargin=2em \labelsep=1em}
\item We use Echo Nest analysis to break a song into a collection of 
beat-chroma ``patches'', typically one or two bars in length.
\item $82\%$ of the bars in our data were 4 beats long.
\item Other cases: we resample patches to a fixed length of 4 beats.
\item We rotate patches so that the first row contains the most energy.
Each patch is normalized independently.
\end{list}

@@

\myfig[0]{song_encoded.ps}{.7}
% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
Exemple of an encoded song (Good Day Sunshine
by \textit{The Beatles}) using a codebook. Codebook size:
$200$, codewords: $2$ bars.
\end{small}
\end{minipage}
\end{center}

\myfig[0]{codes_8bars.ps}{.7}
% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
Longer codewords spanning $8$ bars, randomly selected from
a $100$-entry codebook. Most patterns consist of sustained notes 
or chords, but code 0 shows one-bar alternations between 
two chords, and code 4 contains two cycles of a
$1\rightarrow1\rightarrow1\rightarrow2$ progression.

\end{small}
\end{minipage}
\end{center}

@@

% figure caption
\begin{center}
\begin{minipage}[c]{.7\columnwidth}
\begin{small}
Possible visualization of the codebook using locally linear
embedding (LLE).
\end{small}
\end{minipage}
\end{center}
